Appendix 6: sdmTMB model validation and speed-testing methods

### 2021-12-22 doc/appendix-validation.Rmd
Substantial paper editing

---
title: "Appendix X: sdmTMB validation"
output:
  bookdown::pdf_document2:
    toc: false
number_sections: false
fig_caption: true
highlight: "monochrome"
csl: mee.csl
bibliography: refs.bib
header-includes:
  \usepackage[left]{lineno}
  \usepackage{bm}
  \usepackage{amssymb}
---

>>>>

---
title: "Appendix 6: sdmTMB model validation and speed-testing methods"
output:
  bookdown::pdf_document2:
    toc: false
number_sections: false
fig_caption: true
highlight: "monochrome"
csl: mee.csl
bibliography: refs.bib
header-includes:
  \usepackage[left]{lineno}
  \usepackage{bm}
  \usepackage{amssymb}
---
